An Event-based Architecture for Multi-population Optimization Algorithms

### 2020-01-20 draft.tex
Captions added

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{classicisland}
    \caption{Example of a parametric plot ($\sin (x), \cos(x), x$)}
    \label{fig:kafkEO}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{pool_island}
    \caption{Example of a parametric plot ($\sin (x), \cos(x), x$)}
    \label{fig:kafkEO}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{population_pool}
    \caption{Example of a parametric plot ($\sin (x), \cos(x), x$)}
    \label{fig:kafkEO}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{population_message}
    \caption{Example of a parametric plot ($\sin (x), \cos(x), x$)} % Er, same caption. Better insert it now, or we might roftet... Also, same label. - JJ
    \label{fig:kafkEO}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{experiment_flow}
    \caption{Example of a parametric plot ($\sin (x), \cos(x), x$)}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{worker}
    \caption{Example of a parametric plot ($\sin (x), \cos(x), x$)}
\end{figure}

>>>>

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{classicisland}
    \caption{ Population State and dataflow between processing nodes of a classic Island-based multi-population algorithm. }
    \label{fig:classicisland}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{pool_island}
    \caption{Population State and dataflow between processing nodes of a Pool-based multi-population algorithm.}
    \label{fig:pool_island}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{population_pool}
    \caption{Population State and dataflow between processing nodes of the EvoSpace algorithm.}
    \label{fig:population_pool}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{population_message}
    \caption{Population State and dataflow between processing nodes of the EvoSpace algorithm.} % Er, same caption. Better insert it now, or we might roftet... Also, same label. - JJ
    % Ok, it was a "temporal" Copy-Paste solution - Mario
    \label{fig:population_message}
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{experiment_flow}
    \caption{EvoSwarm Workflow}
\end{figure}

\begin{figure}[h]
    \centering
    \includegraphics[width=\textwidth]{worker}
    \caption{Serverless function implementation details. Showing the worker algorithm in each container}
\end{figure}
